\section{Professional Experience}


% -------------- Swisscom--------------------
\cventry{March '20 -- Present}{Senior Software Engineer}{Swisscom}{Switzerland}{}{\begin{itemize}
  \item Building Swisscom's knowledge graph to improve the B2B customers' end-to-end experience across all Swisscom's products and services.
  \item Designing near-real time streaming ETL pipelines.
  \item Domain analysis and modeling (worked with Networking, Telco, Cloud, IT-inventory, Alerting, and Incidents management domains).
  \item Co/supervised 4 masters students in collaboration with Swisscom Digital Lab and EPFL Lausanne. Their projects were in graph embedding and network modeling.
  \item \emph{Technologies used:} Graph DB, Neo4j, Kafka Streams, Spring Boot, Java, Ansible.
\end{itemize}}


% -------------- ETH--------------------
\cventry{June '15 -- Oct. '19}{Research Assistant}{ETH Z\"urich}{Switzerland}{}{\begin{itemize}
  \item Developed systems to automatically synthesize router configurations from high-level requirements.  \httplink[https://github.com/nsg-ethz/synet-plus]{github.com/nsg-ethz/synet-plus}, \httplink[https://github.com/nsg-ethz/synet]{github.com/nsg-ethz/synet}. Published in \cite{netcomplete, synet-cav, synet-arxiv}.
  \item Developed a system to detect concurrency violations in production-grade controllers of Software-Defined Networks (SDN).  \httplink[https://github.com/nsg-ethz/sdnracer]{github.com/nsg-ethz/sdnracer}. Published in \cite{bigbug, sdnracer2, sdnracer}.
  \item \emph{Technologies used:} Cisco IOS, BGP, OSPF, Python, SDN, Z3 SMT Solver, Git.
\end{itemize}}


% -------------- Facebook--------------------
\cventry{June -- Sept. '18}{Software Engineer Intern}{Facebook}{Menlo Park, CA, USA}{}{\begin{itemize}
  \item Started a practical network verification initiative.
  \item Built a prototype system to verify the correctness of Facebook's network.
  \item \emph{Technologies used:} Python, Thrift, Mercurial.
\end{itemize}}


% -------------- IU 2nd --------------------
\cventry{Jan -- May '15}{Research Associate}{Indiana University}{Bloomington, IN, USA}{}{\begin{itemize}
\item Measured garbage collector and data serialization overhead for unstructured data.
\item Developed efficient method for representing unstructured data in Haskell's runtime system. Published in \cite{cnf}.
\item \emph{Technologies used:} Java,  Continuous Integration/Deployment (CI/CD),Git.
\end{itemize}}

% -------------- ICSI --------------------
\cventry{July '13 -- Nov. '14}{Research Scientist}{International Computer Science Institute (ICSI)}{Berkeley, CA, USA}{}{\begin{itemize}
\item Worked in Prof. Scott Shenker's group on designing and building next-generation SDN architecture (SDNv2).
\item Integrated a research system for quality assurance to run in a production environement with ONOS; a carrier-grade SDN open-source network operating system. \httplink[http://onosproject.org/]{onosproject.org}. Published in \cite{scott2014trooubleshooting}.
%\item Helped ONOS Quality Assurance team adopt parts of STS in their testing infrastructure.
\item \emph{Technologies used:} Python, Java, Continuous Integration (CI), QA, Git.
\end{itemize}}

% -------------- ESnet --------------------
\cventry{May -- July '13}{Summer Student}{Lawrence Berkeley National Lab.}{Berkeley, CA, USA}{}{\begin{itemize}
\item Worked with the Energy Sciences Network (ESnet) team.
\item Developed a scalable multi-domain Network Topology Service for dynamic multi-domain network circuits' setup. \httplink[https://github.com/ahassany/topology-service]{github.com/ahassany/topology-service}
\item \emph{Technologies used:} Java, Jetty, Atmoshper Framework, REST API design, MongoDB.
\end{itemize}}

% -------------- IU --------------------
\cventry{Aug. '11 -- July '13}{Research Associate}{Indiana University}{Bloomington, IN, USA}{}{\begin{itemize}
\item Developed a RESTful Unified Network Information Services (UNIS) to represent topologies for large-scale multi-domain networks. Published in \cite{ahassany2013unis}.
\item Developed instrumentation and monitoring APIs and tools for GENI \httplink[https://www.geni.net]{https://www.geni.net} experiments and physical infrastructure; \httplink[https://github.com/periscope-ps/unis]{github.com/periscope-ps/unis}.
\item \emph{Technologies used:} Java, Python, Tornado, REST API design, MongoDB, Django, Git.
\end{itemize}}

% --------------- SC -- maybe ignore it --------

% -------------- LBL --------------------
\cventry{August '10}{Summer Student}{Lawrence Berkeley National Lab.}{Berkeley, CA, USA}{}{\begin{itemize}
\item Worked at the Center for Enabling Distributed Petascale Computing (CEDPS) project.
\item Developed a system to collect, represent and analyze large scale  monitoring data for high-speed data transfers in DOE networks.
\item \emph{Technologies used:} Python, Tornado, JavaScript, HTML, JQuery, MongoDB, Django.
\end{itemize}}


% -------------- MoG --------------------
\cventry{Feb. '09 -- July '09}{Software Engineer}{Municipality of Gaza}{Gaza, Palestine}{}{\begin{itemize}
\item Designed a system to extract information, categorize, and archive old building permits from the late 1800s.
\item Designed a new business process and the required software for issuing new building permits in Gaza city.
\item Lead a team of 50 civil engineers and 20 data entry persons to implement the project.
\item \emph{Technologies used:} Oracle DB, Visual Basic~.NET, Delphi.
\end{itemize}}


% -------------- PNINA --------------------
\cventry{Dec. '08 -- Mar. '09}{Independent Consultant}{Palestinian National Internet Naming Authority (PNINA)}{Gaza, Palestine}{}{\begin{itemize}
\item Software quality assurance of in-house built system for registering and managing all \emph{.ps} domain names; PNINA is the country code top-level domain (ccTLD) for Palestine.
\item Consulting on deployment and integration for new domain registration system.
\item \emph{Technologies used:} PHP, Perl, PostgreSQL, MySQL, BIND, Apache.
\end{itemize}}

% -------------- Google Summer of Code --------------------
\cventry{June -- Sept '08}{Student Developer}{Google Inc. \& Internet2}{}{Google Summer of Code 2008}{\begin{itemize}
\item This project is sponsored by Google and administrated by Internet2.
\item Designed and developed open source web based configuration tools for perfSONAR-PS.
\item \emph{Technologies used:} Perl, JavaScript, Apache, HTML, CSS, SVN.
\end{itemize}}

% -------------- AfkarIT --------------------
\cventry{Sep. '07 -- Mar. '08}{Software Engineer}{AfkarIT}{}{Gaza, Palestine}{\begin{itemize}
\item Developed operating system level virtual machines monitoring system for VMWare ESX Infrastructure.
\item \emph{Technologies used:} Python, C\#.
\end{itemize}}


% -------------- Ard El-Insan --------------------
\cventry{Sep. '04 -- Oct. '05}{Contractor Software Engineer}{Ard El-Insan}{}{Gaza, Palestine}{\begin{itemize}
\item Developed patients follow-up management system in four clinics for a project sponsored by European Commission's Humanitarian Aid Office (ECHO).
\item \emph{Technologies used:} Visual Basic \mbox{.NET}, Microsoft SQL Server.
\end{itemize}}

